A thesis draft

### 2018-09-24 draft.tex
Add chap 2

 % --- INTRODUCTION ---
\chapter{Introduction}

@@

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools
already present in the market required some tweaking and some integrations,
shifting our goal to create a complete  European Telecommunications Standards
Institutes (ETSI) Management and orchestrator (MANO) testbed instead, following
the specifications suggested in the RFC 7665, thus implementing only the first
three requisites, without digging in the satellite data flow optimization. In 
particular, we discovered how, these tools, were suitable to create ETSI MANO 
and VNFs using virtual machine or exploiting cloud tecnhologies, while they 
were not designed with enough flexibility to integrate with Docker. In the next 
section we are going to take a deep analysis of the cited technologies, in 
order to provide to the reader enough context to be able to understand our 
design choices we are going to describe later.

\section{MANO}

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\end{document}

>>>>

 % --- INTRODUCTION ---
\chapter{Introduction}
\label{chap:intro}

@@

Starting with the first step of creating a MANO able to process incoming data
packets through VNF functions, we encountered that many networking tools
already present in the market required some tweaking and some integrations,
shifting our goal to create a complete  European Telecommunications Standards
Institutes (ETSI) Management and orchestrator (MANO) testbed instead, following
the specifications suggested in the RFC 7665, thus implementing only the first
three requisites, without digging in the satellite data flow optimization. In 
particular, we discovered how, these tools, were suitable to create ETSI MANO 
and VNFs using virtual machine or exploiting cloud tecnhologies, while they 
were not designed with enough flexibility to integrate with Docker. In the next 
chapter we are going to take a deep analysis of the cited technologies, in 
order to provide to the reader enough context to be able to understand our 
design choices we are going to describe later.

\chapter{Project Analysis}
\label{chap:prjan}

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis.

@@

\subsubsection{Other technologies}\todo{Talk somehow of the other tecnhologies}
\paragraph{Openstack}
\paragraph{Openvswitch}
\end{document}
